\subsection*{Under Review}


\years{} Hill, Terrence, \textbf{Kelsey E. Gonzalez}, and Andrew P. Davis. ``The Nastiest Question: Does Population Mobility vary by Political Leadership during the Novel Coronavirus (COVID-19) Pandemic?'' 
\desc{Under Review.}  \\
% Desk Reject SSM 05-01-20 to 05-04-20 (no reviews)
% Desk Reject Health and Place 05-04-20 to 05-15-20 (no reviews)
% Under Review at Soc Perspectives 05-15-20
    % SocSciRes? SocIndicators? Pol&Soc? JHSB? 

\years{} Hill, Terrence, \textbf{Kelsey E. Gonzalez}, and Laura Upenieks. ``Religiosity and Mobility in Aging Populations: A Multi-Level Analysis of the Novel Coronavirus (COVID-19) Pandemic''
\desc{Under Review.} \\
% Rejected at The JGerontology, Series B: Social Sciences on 05-16-20 to 08-11-20 (2 reviews)
% Under Review at the Journal of Aging and Health 08-12-20

\years{} \textbf{Gonzalez, Kelsey E}. ``Explaining Black-White Differences in Happiness: The Intervening Role of Perceived Structural Racism'' 
\desc{Under Review.}  \\
% submitted to ASA on 1-25-20
% rejected at Society and Mental Health on (2-25-20 to 4-09-20)
% Desk Reject at Sociological Forum on (6-03-20 to 06-04-20)
% Under review at Sociological Inquiry on (6-04-20 to ??-??-20)\
    % SPQ short if rejected

\years{}Jang, Beksahn, \textbf{Kelsey E. Gonzalez}, Liwen Zeng, and Daniel E. Martínez. ``Correlates of Panethnic Identification: Assessing similarities and differences among Latinos and Asian Americans in the United States''
\desc{Under Review.} \\
% Desk reject at Journal of Ethnic and Migration Studies (09-02-19 to 11-1-19)
% Reject at Ethnicities (1 reviewer) (11-2-19 to 12-18-19)
% submitted to ASA on 1-26-2020
% Reject at Sociological Forum (03-09-20 to 05-04-20)
% Sociology of Race and Ethnicity (06-11-20 to ??-??-20)

\years{} \textbf{Gonzalez, Kelsey E.}, Rina James, Eric T. Bjorklund and Terrence Hill. ``They Can’t Breathe: County-Level Conservatism and Infrequent Mask Usage during the Novel Coronavirus (COVID-19) Pandemic'' \desc{Under Review.} \\
% Under Review at journal of health and social behavior (9-22-20 to ??-??-20)

%---------------------------------------------------------------------------------------
\subsection*{Working Papers}

\years{} \textbf{Gonzalez, Kelsey E}. ``Visualizing Multinomial Logistic Regression Models through Data Mining''.
\desc{Manuscript in Preparation.} \\
% need to finish debugging and begin writing  
% Use Happiness data because why not

\years{}  \textbf{Gonzalez, Kelsey E}. and Corey Abramson. ``A framework for the Continuation of Mixed Methods Research''. 
\desc{Manuscript in Preparation.} \\

\years{} Martínez, Daniel E., \textbf{Kelsey E. Gonzalez}, and Ricardo Martinez-Schuldt. ``A  Cross-Panel Analysis of Panethnic Label Preferences of Latinos from 2008-2018''.
\desc{Data Collection and Analysis.} \\
% data and writing mixed

\years{} Abramson, Corey and \textbf{Kelsey E. Gonzalez}. ``Logics of Transformation: A computationally-driven conceptual framework for online discussions of bodily transformation''.
\desc{Data Collection and Analysis.}