\section*{Conference Presentations}

\years{2020} 
\textbf{Gonzalez, Kelsey E.} 
``Race, Ideology of Structural Racism, and Happiness.'' 
\emph{American Sociological Association Annual Conference}, Aug 11, 2020.\\
% Section on Medical Sociology Refereed Roundtables: Table 8. Mental Health and Inequality
% Aug 10, 2020


\years{}
Jang, Beksahn, \textbf{Kelsey E. Gonzalez}, Liwen Zeng, and Daniel E. Martínez.
``Correlates of Panethnic Identification: Assessing similarities and differences among Latinos and Asian Americans in the United States.''
\emph{American Sociological Association Annual Conference}, Aug 10, 2020. \\
% Section on Racial and Ethnic Minorities Roundtables: Table 14: Latinos in America
%Aug 10, 2020


\years{}
Martínez, Daniel E. and \textbf{Kelsey E. Gonzalez}. 
``Panethnicity as a Primary Identifier among Latino-Hispanics in the United States.''
\emph{American Sociological Association Annual Conference}, Aug 08, 2020.  \\
%  Regular Paper Session on Latinas, Latinos, Latinx (Latinx Identity Formation)
% Aug 10, 2020


\years{}
\textbf{Gonzalez, Kelsey E.} 
``Utilizing Blockmodeling, Clustering, and Heatmaps to Visualize Multinomial Logistic Regression Models.''
\emph{Stanford Conference on Computational Sociology}, Aug 07, 2020. Poster.  \\
%  Regular Paper Session on Latinas, Latinos, Latinx (Latinx Identity Formation)
% Aug 10, 2020


\years{} 
\textbf{Gonzalez, Kelsey E.} 
``Utilizing Blockmodeling, Clustering, and Heatmaps to Visualize Multinomial Logistic Regression Models.''
\emph{International Network for Social Network Analysis 40th Sunbelt Conference},  July 13, 2020. \\
%June 04, 2020 (applied by 1-31-20, notified 02-28-20)
% Moved to July 13-17 


\begin{comment}
\years{}
Bergesen, Albert and \textbf{Kelsey E. Gonzalez}. 
``Putting the "Geo" back in Geopolitics.'' (non-presenter)
\emph{International Studies Association Annual Conference}, March 25, 2020. Honolulu, HI.
% Cancelled due to Covid-19
% Panel on Geopolitics and International Security.\\ 
% March 25, 2020
\end{comment}

\years{2019}
\textbf{Gonzalez, Kelsey E.} 
``A Method of Data Mining to Visualize Multinomial Logistic Regression Models.''
\emph{Computational Social Science Showcase}, Dec 06, 2019. Tucson, AZ.\\
%Student Showcase.
%Dec 06, 2019


\years{}
\textbf{Gonzalez, Kelsey E.} 
``The Importance of Homophily for Perceived Ethno-Racial Discrimination.'' 
\emph{American Sociological Association Annual Conference}, Aug 11, 2019. Manhattan, NY.\\
% Racial and Ethnic Minorities Roundtables: Understanding Trends in Racial Identity
% Aug 11, 2019


\years{}
Martínez, Daniel E. and \textbf{Kelsey E. Gonzalez}. 
``Hispanic or Latino?: The Sociodemographic Correlates of Panethnic Label Preferences among US Latinos/Hispanics.'' 
\emph{American Sociological Association Annual Conference}, Aug 10, 2019. Manhattan, NY. \\
% Latina/o Section Roundtables: Identity Formation and Experiences
%Aug 10, 2019

\years{2017} \textbf{Gonzalez, Kelsey E.} 
``The Construction of Immigrant Youth Identities: The Impact of Socialisation and School Environments in the Republic of Ireland.'' \emph{Sociology Research Seminar Series of Trinity College, Dublin}, Mar 15, 2017. Dublin, Ireland.\\



%---------------------------------------------------------------------------------

% Old presentations  
\begin{comment}
    \years{2013} \textbf{Gonzalez, Kelsey E.} 
    ``Life Without Water: The Border Dispute between Chile, Bolivia and Peru.'' \emph{Borders, Boundaries, and Peace Undergraduate Research Conference}. Feb 28, 2013. Milwaukee, WI.
\end{comment}


%---------------------------------------------------------------------------------
% Rejected presentations  

\begin{comment}


\end{comment}


%---------------------------------------------------------------------------------

\begin{comment}
\subsection{Conference Panel Organization, Moderation and Commentary}
\years{2020} Presider of the "" Table. Section on . \emph{American Sociological Association Annual Conference}, Aug 08-11. San Francisco, CA.\\

\years{2020} Organizer of the "Data Ethics \& Bias" Panel. \emph{Women in Data Science Tucson Regional Event}, April 17. Tucson, AZ.\\
\end{comment}
